The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-19 Paper_4_version/Article_UV_Mexico.tex
Paper version 4
Little changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors were also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cccc} \hline
    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
    UVI                    & 0.08                           & 9.2               & 0.9               \\
    PM\textsubscript{10}   & -0.10                          & 50.2              & -0.2              \\
    CO                     & -0.08                          & 1.0               & -8.2              \\
    NO\textsubscript{2}    & -0.96                          & 28.6              & -3.4              \\
    O\textsubscript{3}     & -1.05                          & 61.3              & -1.7              \\
    AOD\textsubscript{340} & -0.01                          & 0.6               & -1.6              \\
    SO\textsubscript{2}    & -0.76                          & 8.4               & -9.1              \\
    \hline
  \end{tabular}
  \caption{{{{Trends of UV Index and criteria pollutants over 2000-2019.
                Units: $\mu g/m^3$ for PM$_{10}$, ppm for CO, ppb for SO$_2$, NO$_2$ and O$_3$.}}}}
  \label{table:uvindex}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}
\usepackage{achemso}
\setkeys{acs}{etalmode=truncate,maxauthors=40}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W and 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors were also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cccc} \hline
    Variable               & $\frac{\text{absolute change}}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
    UVI                    & 0.08                                  & 9.2               & 0.9               \\
    PM\textsubscript{10}   & -0.10                                 & 50.2              & -0.2              \\
    CO                     & -0.08                                 & 1.0               & -8.2              \\
    NO\textsubscript{2}    & -0.96                                 & 28.6              & -3.4              \\
    O\textsubscript{3}     & -1.05                                 & 61.3              & -1.7              \\
    AOD\textsubscript{340} & -0.01                                 & 0.6               & -1.6              \\
    SO\textsubscript{2}    & -0.76                                 & 8.4               & -9.1              \\
    \hline
  \end{tabular}
  \caption{{{{Trends of UV Index and criteria pollutants over 2000-2019.
                Units: $\mu g/m^3$ for PM$_{10}$, ppm for CO, ppb for SO$_2$, NO$_2$ and O$_3$.}}}}
  \label{table:uvindex}
\end{table}
